A modelling strategy to improve cacao quality and productivity

### 2021-07-31 papers/model/paper_model.tex
Update paper_model.tex

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{ The aim of this study is predict the best time for harvest cocoa fruits.}

>>>>

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{ Crop modelling can support agronomical decisions of crop production under a range of scenarios improving competitiveness. Cocoa production systems in Latin America has a high importance over social and economic development, facing  the fight against hunger and poverty. Cocoa fruits development can be considered as the result of a number of physiological and morphological processes that can be described by mathematical relationships even under uncontrolled environments. We parametrize the SIMPLE crop model \citep{Zao2019simple} to predict the best time for harvest cocoa fruits in Colombia. The aim of this study is develop a practical tool for farmers using flowering date and weather variables (Solar radiation, rain and temperature) easily available for crop modelling to understand and predict the phenology of cacao trees which is key to produce high quality cacao beans.}
